```{r libraries, error=FALSE, message=FALSE,   echo=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(semanticaxelrod)
library(ggplot2)
library(grid)

theme_set(theme_bw())


load("~/local-research/semanticaxelrod/rawdata/saa12-full.rda")


saa12fullnoinnov <- subset(saa12full, innovation_rate == 0 )
saa12fullinnov <- subset(saa12full, innovation_rate > 0 )

# for cultural differentation
rc <- select(saa12full, simulation_run_id, num_culture_regions, size_trait_space, learning_rate, innovation_rate)
full_region_count <- unique(rc)

rc_by_time <- select(saa12full, simulation_run_id, num_culture_regions, size_trait_space, learning_rate, innovation_rate, sample_time)
rc_by_time_count <- unique(rc_by_time)

rc_by_time_0.9 <- subset(rc_by_time_count, learning_rate == 0.9)

rc2 <- select(saa12fullnoinnov, simulation_run_id, num_culture_regions, size_trait_space, learning_rate, innovation_rate)
rc_noinnov <- unique(rc2)

rc3 <- select(saa12fullinnov, simulation_run_id, num_culture_regions, size_trait_space, learning_rate, innovation_rate)
rc_innov <- unique(rc3)


# subset of data for the conference presentation

cf <- subset(saa12full, size_trait_space == 160 | size_trait_space == 640 | size_trait_space == 2496 | size_trait_space == 62496 )
confsubset <- subset(cf, learning_rate == 0.1 | learning_rate == 0.4 | learning_rate == 0.9)
rc4 <- select(confsubset, simulation_run_id, num_culture_regions, size_trait_space, learning_rate)
confsubset_region_count <- unique(rc4)

```


Is there a systematic relationship between the number of culture regions in a sample and the learning rate, at a given size design space?

```{r culture-regions, results="asis", message=FALSE, warning=FALSE, fig.width=12}


# THIS FIGURE IS USED IN THE SPRINGER PAPER

p <- ggplot(full_region_count, aes(x=num_culture_regions)) + geom_histogram(binwidth=5, fill="darkgrey") + xlab("Number of Distinct Cultural Configurations") + ggtitle("Size Spectrum of Cultures by Size of the Design Space (horizontal) and Learning Rate (vertical)")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y", as.table=FALSE)
ggsave("../paper/figure/size-spectrum-regions-saa12full.pdf", dpi=300)


```

And, a subset which is small enough to be legible for the conference presentation:

```{r culture-regions-conf, results="asis", message=FALSE, warning=FALSE, fig.width=12}


# THIS FIGURE IS USED IN THE CONF PAPER

p <- ggplot(confsubset_region_count, aes(x=num_culture_regions)) + geom_histogram(binwidth=5, fill="#39275B") + xlab("Number of Distinct Cultural Configurations") + ggtitle("Size Spectrum of Cultures by Size of the Design Space (horizontal) and Learning Rate (vertical)")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y", as.table=FALSE)
ggsave("../presentation/images/conf-size-spectrum-regions-saa12full.pdf", dpi=300)


```





How does the mutation or innovation rate affect this?  First, without innovation:


```{r culture-regions2, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(rc_noinnov, aes(x=num_culture_regions)) + geom_histogram(fill="darkgrey", binwidth=1) + xlab("Number of Distinct Cultural Configurations") + ggtitle("Size Spectrum of Cultures by Size of the Design Space (horizontal) and Learning Rate (vertical)")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y", as.table=FALSE)

```

And, with innovation:

```{r culture-regions3, results="asis", message=FALSE, warning=FALSE, fig.width=12}

p <- ggplot(rc_innov, aes(x=num_culture_regions)) + geom_histogram(fill="darkgrey", binwidth=5) + xlab("Number of Distinct Cultural Configurations") + ggtitle("Size Spectrum of Cultures by Size of the Design Space (horizontal) and Learning Rate (vertical)")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y", as.table=FALSE)



```

Now, let's look at the distribution of monocultural solutions:

```{r culture-regions4, results="asis", message=FALSE, warning=FALSE, fig.width=12}

monocultural_both <- subset(full_region_count, num_culture_regions == 1)
p <- ggplot(monocultural_both, aes(x=learning_rate)) + geom_histogram(fill="darkgrey") + ggtitle("Occcurrence of Monocultural Solutions by Learning Rate")
p + facet_grid(size_trait_space ~ ., , as.table=FALSE)



```


Time dependence?

```{r time-1, results="asis", message=FALSE, warning=FALSE, fig.width=12}

p <- ggplot(rc_by_time_0.9, aes(x=num_culture_regions)) + geom_histogram(binwidth=5, fill="darkgrey") + xlab("Number of Distinct Cultural Configurations") + ggtitle("Size Spectrum of Cultures by Size of the Design Space (horizontal) and Learning Rate (vertical)")
p + facet_grid(sample_time ~ size_trait_space, scale="free_y", as.table=FALSE)
```





And we can look at the linear model.  We only have a few values of learning rate and innovation rate, but technically both are continuous variables, as is the response variable.  Here I look at the innovation set only.

```{r lm-1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
fit <- lm(num_culture_regions ~ learning_rate + innovation_rate + size_trait_space, data=rc_innov)
summary(fit)
```




