# SAA-2, SAA-3, SAA-4, SAA-7 EDA:  Small State Space #

```{r libraries, error=FALSE, message=FALSE,   echo=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(semanticaxelrod)
library(ggplot2)

load("data/saa_finalized_combined.rda")

smallstate100 <- subset(saa_finalized_combined, branching_factor == 3 & depth_factor == 3 & population_size == 100)


```

To start, I'm looking just at the size 100 population, and the "smallest" trait trees, $r=3, h=3$.  


```{r eda-orbit, results="asis", message=FALSE, warning=FALSE}
qplot(orbit_number, data=smallstate100, geom="density", binwidth=2) + facet_grid(learning_rate ~ num_trait_trees)
```

There does seem to be interesting variation in orbit number across learning rates, and in state spaces that have different numbers of trees (choices here are 4, 8, 16).  Let's see if there is significant difference in the CI's:

```{r eda-sss-orbit-box, results="asis", message=FALSE, warning=FALSE}

ss4 <- subset(smallstate100, num_trait_trees == 4)
p <- ggplot(ss4, aes(factor(learning_rate), orbit_number))
p + geom_boxplot(notch=TRUE)

```



Continuing with other metrics.  


```{r eda-autgroupsize, results="asis", message=FALSE, warning=FALSE}
qplot(log(autgroupsize), data=smallstate100, geom="density", binwidth=2) + facet_grid(learning_rate ~ num_trait_trees)
```

The hints of bimodality are very interesting, as is the sense that the distribution is spreading with population size and learning rate.

```{r eda-lambda, results="asis", message=FALSE, warning=FALSE}
qplot(msg_lambda, data=smallstate100, geom="density", binwidth=0.05) + facet_grid(learning_rate ~ num_trait_trees)
```

Lambda is a statistic which measures the fraction of vertices that belong to "non-trivial" orbits -- i.e., orbits with multiplicities greater than one.  There seems to be little interesting variation here, except that the modes near 0 and 1 might again by initialization effects.  

```{r eda-beta, results="asis", message=FALSE, warning=FALSE}
qplot(mem_beta, data=smallstate100, geom="density", binwidth=0.05) + facet_grid(learning_rate ~ num_trait_trees)
```

Beta (here, calculated with n-1! as the denominator) is the n-th root of the ratio of the automorphism group order to the maximally symmetric automorophism group (a tree with n-1 leaves).  A better solution is to normalize against the starting tree for each configuration, in log space, but I don't have that in this data set yet.  This isn't terribly interesting, since the resulting trait trees are all very similar in many respects.  

```{r eda-radius, results="asis", message=FALSE, warning=FALSE}
qplot(radius_frac, data=smallstate100, geom="density", binwidth=0.05) + facet_grid(learning_rate ~ num_trait_trees)
```

Mean degree:

```{r eda-degree, results="asis", message=FALSE, warning=FALSE}
qplot(mean_degree, data=smallstate100, geom="density", binwidth=0.05) + facet_grid(learning_rate ~ num_trait_trees)
```

Remaining density:

```{r eda-density, results="asis", message=FALSE, warning=FALSE}
qplot(remaining_density, data=smallstate100, geom="density", binwidth=0.01) + facet_grid(learning_rate ~ num_trait_trees)
```


mean_orbit_multiplicity:

```{r eda-orbitmult, results="asis", message=FALSE, warning=FALSE}
qplot(mean_orbit_multiplicity, data=smallstate100, geom="density", binwidth=0.5) + facet_grid(learning_rate ~ num_trait_trees)
```
