```{r libraries, error=FALSE, message=FALSE,   echo=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(semanticaxelrod)
library(ggplot2)

load("~/local-research/semanticaxelrod/rawdata/saa12-final.rda")

ss5516 <- subset(saa12final, size_trait_space == 62496)
ss3316 <- subset(saa12final, size_trait_space == 640)
ss16 <- subset(saa12final, num_trait_trees == 16)

ss16midinnov <- subset(ss16, innovation_rate == 5e-05)
rc <- select(ss16midinnov, simulation_run_id, num_culture_regions, size_trait_space, learning_rate)
ss16mid_region_count <- unique(rc)

ss16midnoinnov <- subset(ss16, innovation_rate == 0)
rc2 <- select(ss16midnoinnov, simulation_run_id, num_culture_regions, size_trait_space, learning_rate)
ss16mid_region_count_noinnov <- unique(rc2)

```

There's very definitely some interesting stuff happening with the remaining density if we look in a single size of state space -- in this case, our largest.  

```{r density1, results="asis", message=FALSE, warning=FALSE, fig.width=12}

p <- ggplot(data=ss5516, aes(y=remaining_density, x=factor(learning_rate), fill=factor(innovation_rate)))
p + geom_boxplot(notch=FALSE)

```
And, at a much smaller state space, we see the same shape but at a much higher fraction of remaining density.  

```{r density2, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(data=ss3316, aes(y=remaining_density, x=factor(learning_rate), fill=factor(innovation_rate)))
p + geom_boxplot(notch=FALSE)

```

## 16 Trees, Low Innovation Level ##
Now, let's just look at the state spaces with 16 trees, and with the medium level of innovation, 5e-05.  
Now let's look at the radius fraction.  Again, these all have 16 trait trees, but some of them are depth 3 and some depth 5.  So what's interesting is the ratio to the maximum.  This seems like a clear effect, but with the size of the state space, the entire pattern just shifts left, to occupy less of the state space.  

```{r rad1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(ss16midinnov, aes(x=radius_frac)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")

```

Finally let's see what's going on with symmetry measures.  First, the raw orbit number:

```{r orb1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(ss16midinnov, aes(x=orbit_number)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")

```

And now the lambda function:

```{r lamb1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(ss16midinnov, aes(x=msg_lambda)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")

```

And now the automorphism group size:

```{r autg1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(ss16midinnov, aes(x=log(autgroupsize))) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")

```

How does the final tree size compare?  


```{r order1, results="asis", message=FALSE, warning=FALSE, fig.width=12}
p <- ggplot(ss16midinnov, aes(x=order)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")

```

## Number of Cultural Regions ##

Here, we take the subset of data which has 16 trait trees, and innovation rate of 5e-05, and do the unique cultural solutions aggregation.  Then, we can look at the results faceted by the overall size of the state space, and the learning rate.  

```{r culture-regions, results="asis", message=FALSE, warning=FALSE, fig.width=12}

p <- ggplot(ss16mid_region_count, aes(x=num_culture_regions)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")


```

```{r culture-regions-noinnov, results="asis", message=FALSE, warning=FALSE, fig.width=12}

p <- ggplot(ss16mid_region_count_noinnov, aes(x=num_culture_regions)) + geom_density(fill="red")
p + facet_grid(learning_rate ~ size_trait_space, scale="free_y")


```


ss16mid_region_count_noinnov


